---
title: "TIME Project - Instagram Data Collection"
author: "Scott I. Donaldson, PhD"
date: "6/14/2021"
output: 
  html_notebook: 
    toc: yes
editor_options: 
  chunk_output_type: inline
---

# Application Programming Interface

Download the Real Instagram Package package and connect to the unofficial Instagram API.

```{r Packages}
setwd("~/Desktop/USC/TIME/R/TIME")
library(Rinstapkg)
library(tidyverse)
library(readxl)
library(knitr)
```

```{r Instagram API}
#Rinstapkg Authentication
ig_auth(username = "scott_donaldson_phd",
        password = "Big5Air6$")

```

# Social Media Analytics

Create a series of search terms to identify appropriate hashtags within each search. For TIME, we will probably want to create a selection criteria of hashtags that have N number of posts.

# Search Tags

```{r Juul Search Tags, echo=TRUE}
# Search Tags
JuulSearch      <- ig_search_tags("swisher")
```

# Juul
### Hashtags for Juul {style="color: blue"}

1.  juulpods

2.  juulmemes

3.  juulgang

4.  juulvapor

5.  juuling

6.  juultricks

7.  juulcentral

8.  juullife

9.  juulpod

10. juuls

#### Juulpods {style="color: purple"}

Search the feed for the juulpods hashtag

```{r Get juulpods hashtag, echo=TRUE}
Juulpods <- ig_get_hashtag_feed("juulpods")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose Juulpods lists and create final df, echo=TRUE}

# Decompose list variables in the data
Juulpods_caption <- items_to_tidy_df(Juulpods$caption)
Juulpods_user    <- items_to_tidy_df(Juulpods$user)

JuulPods_FinalDF <- cbind(Juulpods,
                          Juulpods_caption,
                          Juulpods_user)

                        
```

```{r Subset final juulpods df}
JuulPods_FinalDF <- JuulPods_FinalDF %>% select(code,
                                                username,
                                                taken_at,
                                                text,
                                                comment_count,
                                                like_count,
                                                view_count)

JuulPods_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
JuulPods_FinalDF$URLLINK <- paste(JuulPods_FinalDF$Insta,JuulPods_FinalDF$code,
                                sep = "")
JuulPods_FinalDF <- JuulPods_FinalDF %>% select(-Insta,
                                                  -code)
```

```{r Date variable juulpods}
#Clean Date Variable
JuulPods_FinalDF$taken_at <- as_epoch(JuulPods_FinalDF$taken_at)
JuulPods_FinalDF$taken_at <-as.Date(as.POSIXct(JuulPods_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juul pods}
#Rename Variables
JuulPods_FinalDF <- JuulPods_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juulpods, echo=TRUE}
write_csv(JuulPods_FinalDF, "JuulPods_FinalDF.csv")
```

#### Juulmemes {style="color: purple"}

Search the feed for the juulmemes hashtag

```{r Get juulmemes hashtag, echo=TRUE}
juulmemes <- ig_get_hashtag_feed("juulmemes")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juulmemes lists and create final df, echo=TRUE}

# Decompose list variables in the data
juulmemes_caption <- items_to_tidy_df(juulmemes$caption)
juulmemes_user    <- items_to_tidy_df(juulmemes$user)

juulmemes_FinalDF <- cbind(juulmemes,
                          juulmemes_caption,
                          juulmemes_user)


```


```{r Subset final juulmemes df}
juulmemes_FinalDF <- juulmemes_FinalDF %>% select(code,
                                                username,
                                                taken_at,
                                                text,
                                                comment_count,
                                                like_count,
                                                view_count,
                                                play_count)

juulmemes_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juulmemes_FinalDF$URLLINK <- paste(juulmemes_FinalDF$Insta,juulmemes_FinalDF$code,
                                sep = "")
juulmemes_FinalDF <- juulmemes_FinalDF %>% select(-Insta,
                                                  -code)
```

```{r Date variable juulmemes}
#Clean Date Variable
juulmemes_FinalDF$taken_at <- as_epoch(juulmemes_FinalDF$taken_at)
juulmemes_FinalDF$taken_at <-as.Date(as.POSIXct(juulmemes_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juulmemes}
#Rename Variables
juulmemes_FinalDF <- juulmemes_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juulmemes, echo=TRUE}
write_csv(juulmemes_FinalDF, "juulmemes_FinalDF.csv")
```


#### Juulgang {style="color: purple"}

Search the feed for the juulgang hashtag

```{r Get juulgang hashtag, echo=TRUE}
juulgang <- ig_get_hashtag_feed("juulgang")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juulgang lists and create final df, echo=TRUE}
# Decompose list variables in the data
juulgang_caption <- items_to_tidy_df(juulgang$caption)
juulgang_user    <- items_to_tidy_df(juulgang$user)

juulgang_FinalDF <- cbind(juulgang,
                          juulgang_caption,
                          juulgang_user)
```


```{r Subset final juulgang df}
juulgang_FinalDF <- juulgang_FinalDF %>% select(code,
                                                username,
                                                taken_at,
                                                text,
                                                comment_count,
                                                like_count,
                                                view_count,
                                                play_count)

juulgang_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juulgang_FinalDF$URLLINK <- paste(juulgang_FinalDF$Insta,juulgang_FinalDF$code,
                                sep = "")
juulgang_FinalDF <- juulgang_FinalDF %>% select(-Insta,
                                                  -code)
```

```{r Date variable juulgang}
#Clean Date Variable
juulgang_FinalDF$taken_at <- as_epoch(juulgang_FinalDF$taken_at)
juulgang_FinalDF$taken_at <-as.Date(as.POSIXct(juulgang_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juulgang}
#Rename Variables
juulgang_FinalDF <- juulgang_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juulgang, echo=TRUE}
write_csv(juulgang_FinalDF, "juulgang_FinalDF.csv")
```

#### Juulvapor {style="color: purple"}

Search the feed for the juulvapor hashtag

```{r Get juulvapor hashtag, echo=TRUE}
juulvapor <- ig_get_hashtag_feed("juulvapor")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juulvapor lists and create final df, echo=TRUE}

# Decompose list variables in the data
juulvapor_caption <- items_to_tidy_df(juulvapor$caption)
juulvapor_user    <- items_to_tidy_df(juulvapor$user)

juulvapor_FinalDF <- cbind(juulvapor,
                          juulvapor_caption,
                          juulvapor_user)

```

```{r Subset final juulvapor df}
juulvapor_FinalDF <- juulvapor_FinalDF %>% select(code,
                                                username,
                                                taken_at,
                                                text,
                                                comment_count,
                                                like_count,
                                                view_count,
                                                play_count)

juulvapor_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juulvapor_FinalDF$URLLINK <- paste(juulvapor_FinalDF$Insta,juulvapor_FinalDF$code,
                                sep = "")
juulvapor_FinalDF <- juulvapor_FinalDF %>% select(-Insta,
                                                  -code)
```

```{r Date variable juulvapor}
#Clean Date Variable
juulvapor_FinalDF$taken_at <- as_epoch(juulvapor_FinalDF$taken_at)
juulvapor_FinalDF$taken_at <-as.Date(as.POSIXct(juulvapor_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juulvapor}
#Rename Variables
juulvapor_FinalDF <- juulvapor_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juulvapor, echo=TRUE}
write_csv(juulvapor_FinalDF, "juulvapor_FinalDF.csv")
```

#### Juuling {style="color: purple"}

Search the feed for the juuling hashtag

```{r Get juuling hashtag, echo=TRUE}
juuling <- ig_get_hashtag_feed("juuling")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juuling lists and create final df, echo=TRUE}

# Decompose list variables in the data
juuling_caption <- items_to_tidy_df(juuling$caption)
juuling_user    <- items_to_tidy_df(juuling$user)

juuling_FinalDF <- cbind(juuling,
                          juuling_caption,
                          juuling_user)

```

```{r Subset final juuling df}
juuling_FinalDF <- juuling_FinalDF %>% select(code,
                                              username,
                                              taken_at,
                                              text,
                                              comment_count,
                                              like_count,
                                              view_count,
                                              play_count)

juuling_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juuling_FinalDF$URLLINK <- paste(juuling_FinalDF$Insta,juuling_FinalDF$code,
                                sep = "")
juuling_FinalDF <- juuling_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable juuling}
#Clean Date Variable
juuling_FinalDF$taken_at <- as_epoch(juuling_FinalDF$taken_at)
juuling_FinalDF$taken_at <-as.Date(as.POSIXct(juuling_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juuling}
#Rename Variables
juuling_FinalDF <- juuling_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juuling, echo=TRUE}
write_csv(juuling_FinalDF, "juuling_FinalDF.csv")

```

#### Juultricks {style="color: purple"}

Search the feed for the juultricks hashtag

```{r Get juultricks hashtag, echo=TRUE}
juultricks <- ig_get_hashtag_feed("juultricks")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juultricks lists and create final df, echo=TRUE}

# Decompose list variables in the data
juultricks_caption <- items_to_tidy_df(juultricks$caption)
juultricks_user    <- items_to_tidy_df(juultricks$user)

juultricks_FinalDF <- cbind(juultricks,
                          juultricks_caption,
                          juultricks_user)

```

```{r Subset final juultricks df}
juultricks_FinalDF <- juultricks_FinalDF %>% select(code,
                                                username,
                                                taken_at,
                                                text,
                                                comment_count,
                                                like_count,
                                                view_count,
                                                play_count)

juultricks_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juultricks_FinalDF$URLLINK <- paste(juultricks_FinalDF$Insta,juultricks_FinalDF$code,
                                sep = "")
juultricks_FinalDF <- juultricks_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable juultricks}
#Clean Date Variable
juultricks_FinalDF$taken_at <- as_epoch(juultricks_FinalDF$taken_at)
juultricks_FinalDF$taken_at <-as.Date(as.POSIXct(juultricks_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juultricks}
#Rename Variables
juultricks_FinalDF <- juultricks_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juultricks, echo=TRUE}
write_csv(juultricks_FinalDF, "juultricks_FinalDF.csv")

```

#### Juulcentral {style="color: purple"}

Search the feed for the juulcentral hashtag

```{r Get juulcentral hashtag, echo=TRUE}
juulcentral <- ig_get_hashtag_feed("juulcentral")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juulcentral lists and create final df, echo=TRUE}

# Decompose list variables in the data
juulcentral_caption <- items_to_tidy_df(juulcentral$caption)
juulcentral_user    <- items_to_tidy_df(juulcentral$user)

juulcentral_FinalDF <- cbind(juulcentral,
                          juulcentral_caption,
                          juulcentral_user)

```

```{r Subset final juulcentral df}
juulcentral_FinalDF <- juulcentral_FinalDF %>% select(code,
                                                username,
                                                taken_at,
                                                text,
                                                comment_count,
                                                like_count,
                                                view_count)
                                                #play_count

juulcentral_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juulcentral_FinalDF$URLLINK <- paste(juulcentral_FinalDF$Insta,juulcentral_FinalDF$code,
                                sep = "")
juulcentral_FinalDF <- juulcentral_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable juulcentral}
#Clean Date Variable
juulcentral_FinalDF$taken_at <- as_epoch(juulcentral_FinalDF$taken_at)
juulcentral_FinalDF$taken_at <-as.Date(as.POSIXct(juulcentral_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juulcentral}
#Rename Variables
juulcentral_FinalDF <- juulcentral_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juulcentral, echo=TRUE}
write_csv(juulcentral_FinalDF, "juulcentral_FinalDF.csv")
```

#### Juullife {style="color: purple"}

Search the feed for the juullife hashtag

```{r Get juullife hashtag, echo=TRUE}
juullife <- ig_get_hashtag_feed("juullife")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juullife lists and create final df, echo=TRUE}

# Decompose list variables in the data
juullife_caption <- items_to_tidy_df(juullife$caption)
juullife_user    <- items_to_tidy_df(juullife$user)

juullife_FinalDF <- cbind(juullife,
                          juullife_caption,
                          juullife_user)

```

```{r Subset final juullife df}
juullife_FinalDF <- juullife_FinalDF %>% select(code,
                                                username,
                                                taken_at,
                                                text,
                                                comment_count,
                                                like_count,
                                                view_count,
                                                play_count)

juullife_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juullife_FinalDF$URLLINK <- paste(juullife_FinalDF$Insta,juullife_FinalDF$code,
                                sep = "")
juullife_FinalDF <- juullife_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable juullife}
#Clean Date Variable
juullife_FinalDF$taken_at <- as_epoch(juullife_FinalDF$taken_at)
juullife_FinalDF$taken_at <-as.Date(as.POSIXct(juullife_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juullife}
#Rename Variables
juullife_FinalDF <- juullife_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juullife, echo=TRUE}
write_csv(juullife_FinalDF, "juullife_FinalDF.csv")
```

#### Juulpod{style="color: purple"}

Search the feed for the juulpod hashtag

```{r Get juulpod hashtag, echo=TRUE}
juulpod <- ig_get_hashtag_feed("juulpod")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juulpod lists and create final df, echo=TRUE}

# Decompose list variables in the data
juulpod_caption <- items_to_tidy_df(juulpod$caption)
juulpod_user    <- items_to_tidy_df(juulpod$user)

juulpod_FinalDF <- cbind(juulpod,
                          juulpod_caption,
                          juulpod_user)

```

```{r Subset final juulpod df}
juulpod_FinalDF <- juulpod_FinalDF %>% select(code,
                                              username,
                                              taken_at,
                                              text,
                                              comment_count,
                                              like_count,
                                              view_count)

juulpod_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juulpod_FinalDF$URLLINK <- paste(juulpod_FinalDF$Insta,juulpod_FinalDF$code,
                                sep = "")
juulpod_FinalDF <- juulpod_FinalDF %>% select(-Insta,
                                              -code)

```

```{r Date variable juulpod}
#Clean Date Variable
juulpod_FinalDF$taken_at <- as_epoch(juulpod_FinalDF$taken_at)
juulpod_FinalDF$taken_at <-as.Date(as.POSIXct(juulpod_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juulpod}
#Rename Variables
juulpod_FinalDF <- juulpod_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juulpod, echo=TRUE}
write_csv(juulpod_FinalDF, "juulpod_FinalDF.csv")
```


#### Juuls{style="color: purple"}

Search the feed for the juuls hashtag

```{r Get juuls hashtag, echo=TRUE}
juuls <- ig_get_hashtag_feed("juuls")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose juuls lists and create final df, echo=TRUE}
# Decompose list variables in the data
juuls_caption <- items_to_tidy_df(juuls$caption)
juuls_user    <- items_to_tidy_df(juuls$user)

juuls_FinalDF <- cbind(juuls,
                          juuls_caption,
                          juuls_user)

```

```{r Subset final juuls df}
juuls_FinalDF <- juuls_FinalDF %>% select(code,
                                          username,
                                          taken_at,
                                          text,
                                          comment_count,
                                          like_count,
                                          view_count,
                                          play_count)

juuls_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
juuls_FinalDF$URLLINK <- paste(juuls_FinalDF$Insta,juuls_FinalDF$code,
                                sep = "")
juuls_FinalDF <- juuls_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable juuls}
#Clean Date Variable
juuls_FinalDF$taken_at <- as_epoch(juuls_FinalDF$taken_at)
juuls_FinalDF$taken_at <-as.Date(as.POSIXct(juuls_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables juuls}
#Rename Variables
juuls_FinalDF <- juuls_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for juuls, echo=TRUE}
write_csv(juuls_FinalDF, "juuls.csv")
```


# Ejuice
#### ejuice{style="color: purple"}

Search the feed for the ejuice hashtag

```{r Get ejuice hashtag, echo=TRUE}
ejuice <- ig_get_hashtag_feed("ejuice")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose ejuice lists and create final df, echo=TRUE}
# Decompose list variables in the data
ejuice_caption <- items_to_tidy_df(ejuice$caption)
ejuice_user    <- items_to_tidy_df(ejuice$user)

ejuice_FinalDF <- cbind(ejuice,
                          ejuice_caption,
                          ejuice_user)

```

```{r Subset final ejuice df}
ejuice_FinalDF <- ejuice_FinalDF %>% select(code,
                                            username,
                                            taken_at,
                                            text,
                                            comment_count,
                                            like_count,
                                            view_count,
                                            play_count)

ejuice_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
ejuice_FinalDF$URLLINK <- paste(ejuice_FinalDF$Insta,ejuice_FinalDF$code,
                                sep = "")
ejuice_FinalDF <- ejuice_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable ejuice}
#Clean Date Variable
ejuice_FinalDF$taken_at <- as_epoch(ejuice_FinalDF$taken_at)
ejuice_FinalDF$taken_at <-as.Date(as.POSIXct(ejuice_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables ejuice}
#Rename Variables
ejuice_FinalDF <- ejuice_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for ejuice, echo=TRUE}
write_csv(ejuice_FinalDF, "ejuice_FinalDF.csv")

```


# eliquid
#### eliquid{style="color: purple"}

Search the feed for the eliquid hashtag

```{r Get eliquid hashtag, echo=TRUE}
eliquid <- ig_get_hashtag_feed("eliquid")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose eliquid lists and create final df, echo=TRUE}

# Decompose list variables in the data
eliquid_caption <- items_to_tidy_df(eliquid$caption)
eliquid_user    <- items_to_tidy_df(eliquid$user)

eliquid_FinalDF <- cbind(eliquid,
                          eliquid_caption,
                          eliquid_user)

```

```{r Subset final eliquid df}
eliquid_FinalDF <- eliquid_FinalDF %>% select(code,
                                              username,
                                              taken_at,
                                              text,
                                              comment_count,
                                              like_count,
                                              view_count,
                                              play_count)

eliquid_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
eliquid_FinalDF$URLLINK <- paste(eliquid_FinalDF$Insta,eliquid_FinalDF$code,
                                sep = "")
eliquid_FinalDF <- eliquid_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable eliquid}
#Clean Date Variable
eliquid_FinalDF$taken_at <- as_epoch(eliquid_FinalDF$taken_at)
eliquid_FinalDF$taken_at <-as.Date(as.POSIXct(eliquid_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables eliquid}
#Rename Variables
eliquid_FinalDF <- eliquid_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for eliquid, echo=TRUE}
write_csv(eliquid_FinalDF, "eliquid_FinalDF.csv")
```

# swisher
#### swisher{style="color: purple"}

Search the feed for the swisher hashtag

```{r Get swisher hashtag, echo=TRUE}
swisher <- ig_get_hashtag_feed("swisher")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose swisher lists and create final df, echo=TRUE}
# Decompose list variables in the data
swisher_caption <- items_to_tidy_df(swisher$caption)
swisher_user    <- items_to_tidy_df(swisher$user)

swisher_FinalDF <- cbind(swisher,
                          swisher_caption,
                          swisher_user)

```


```{r Subset final swisher df}
swisher_FinalDF <- swisher_FinalDF %>% select(code,
                                              username,
                                              taken_at,
                                              text,
                                              comment_count,
                                              like_count,
                                              view_count,
                                              play_count)

swisher_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
swisher_FinalDF$URLLINK <- paste(swisher_FinalDF$Insta,swisher_FinalDF$code,
                                sep = "")
swisher_FinalDF <- swisher_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable swisher}
#Clean Date Variable
swisher_FinalDF$taken_at <- as_epoch(swisher_FinalDF$taken_at)
swisher_FinalDF$taken_at <-as.Date(as.POSIXct(swisher_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables swisher}
#Rename Variables
swisher_FinalDF <- swisher_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for swisher, echo=TRUE}
write_csv(swisher_FinalDF, "swisher_FinalDF.csv")
```

# backwoods
#### backwoods{style="color: purple"}

Search the feed for the backwoods hashtag

```{r Get backwoods hashtag, echo=TRUE}
backwoods <- ig_get_hashtag_feed("backwoods")
```

The caption and user variables are in a deeply nested list. Use the items_to_tidy_df function to flatten the lists. Then, create final df.

```{r Decompose backwoods lists and create final df, echo=TRUE}

# Decompose list variables in the data
backwoods_caption <- items_to_tidy_df(backwoods$caption)
backwoods_user    <- items_to_tidy_df(backwoods$user)

backwoods_FinalDF <-merge(backwoods, backwoods_caption, by = 0, all = TRUE)[-1]

backwoods_FinalDF <-merge(backwoods_FinalDF, backwoods_user, by = 0, all = TRUE)[-1]

```


```{r Subset final backwoods df}
backwoods_FinalDF <- backwoods_FinalDF %>% select(code,
                                                username,
                                                taken_at,
                                                text,
                                                comment_count,
                                                like_count,
                                                view_count,
                                                play_count)

backwoods_FinalDF$Insta <- as.character("https://www.instagram.com/p/")
backwoods_FinalDF$URLLINK <- paste(backwoods_FinalDF$Insta,backwoods_FinalDF$code,
                                sep = "")
backwoods_FinalDF <- backwoods_FinalDF %>% select(-Insta,
                                              -code)
```

```{r Date variable backwoods}
#Clean Date Variable
backwoods_FinalDF$taken_at <- as_epoch(backwoods_FinalDF$taken_at)
backwoods_FinalDF$taken_at <-as.Date(as.POSIXct(backwoods_FinalDF$taken_at, origin="1970-01-01"))
```

```{r Rename variables backwoods}
#Rename Variables
backwoods_FinalDF <- backwoods_FinalDF %>%
                    rename(caption = text,
                           date    = taken_at) 
```

Write CSV

```{r Write CSV for backwoods, echo=TRUE}
write_csv(backwoods_FinalDF, "backwoods_FinalDF.csv")
```

